How not to constructivize cohomology

### 2018-10-15 slides-cambridge2016.tex
use https where possible

\note{
  Photo source:
  \href{http://www.stpaulscambridge.org.uk/classes-and-room-hire/activities-and-events/newtown-news/}{Newtown
  News}
}

@@

\note{\justifying
  Details on this point of view can be found in one of Peter Arndt's very nice
  answers on MathOverflow:
  \begin{center}\url{http://mathoverflow.net/a/14334/31233}\end{center}
  \par
}

@@

    \item \begin{justify}For expositions of the internal language,
    see Chapters~D1 to~D4 of the Elephant, Chapter~VI of Moerdijk and Mac
    Lane's book, or Chapter~13 of
    \href{http://www.mathematik.tu-darmstadt.de/~streicher/CTCL.pdf}{these
    lecture notes by Thomas Streicher}.\end{justify}
  \end{itemize}
}

@@

\note{\justifying
  The axioms of a prime filter constitute a propositional geometric theory.
  Therefore there exists the \emph{classifying locale} over prime filters. This
  is the ring's spectrum. See Vicker's
  \href{http://www.cs.bham.ac.uk/~sjv/LocTopSpaces.pdf}{Locales and Toposes as Spaces} and
  \href{http://www.cs.bham.ac.uk/~sjv/GeoAspects.pdf}{Continuity and geometric
  logic} for very accessible introductions to this topic.

@@

  \centering
  \hil{\href{http://tiny.cc/topos-notes}{http://tiny.cc/topos-notes}}
  \par
\end{frame}

>>>>

\note{
  Photo source:
  \href{https://www.stpaulscambridge.org.uk/classes-and-room-hire/activities-and-events/newtown-news/}{Newtown
  News}
}

@@

\note{\justifying
  Details on this point of view can be found in one of Peter Arndt's very nice
  answers on MathOverflow:
  \begin{center}\url{https://mathoverflow.net/a/14334/31233}\end{center}
  \par
}

@@

    \item \begin{justify}For expositions of the internal language,
    see Chapters~D1 to~D4 of the Elephant, Chapter~VI of Moerdijk and Mac
    Lane's book, or Chapter~13 of
    \href{https://www.mathematik.tu-darmstadt.de/~streicher/CTCL.pdf}{these
    lecture notes by Thomas Streicher}.\end{justify}
  \end{itemize}
}

@@

\note{\justifying
  The axioms of a prime filter constitute a propositional geometric theory.
  Therefore there exists the \emph{classifying locale} over prime filters. This
  is the ring's spectrum. See Vicker's
  \href{https://www.cs.bham.ac.uk/~sjv/LocTopSpaces.pdf}{Locales and Toposes as Spaces} and
  \href{https://www.cs.bham.ac.uk/~sjv/GeoAspects.pdf}{Continuity and geometric
  logic} for very accessible introductions to this topic.

@@

  \centering
  \hil{\href{https://tiny.cc/topos-notes}{http://tiny.cc/topos-notes}}
  \par
\end{frame}

### 2018-10-15 slides-pssl104.tex
use https where possible

  An informative and entertaining primer on constructive mathematics can be
  found in the linked talk recording by Andrej Bauer or his
  \fixedhref{http://www.ams.org/journals/bull/2017-54-03/S0273-0979-2016-01556-4/S0273-0979-2016-01556-4.pdf}{written
  notes} on the subject. Don't worry, the standard proof that~$\sqrt{2}$ is not rational is
  perfectly fine in constructive mathematics.
  }
\end{frame}

@@

  \begin{itemize}
    \small
    \item It's consistent with \textbf{ZF} that there are no injective modules
    \href{http://www.ams.org/journals/tran/1979-255-00/S0002-9947-1979-0542870-6/S0002-9947-1979-0542870-6.pdf}{[Blass 1979]}.
    \item The existence of enough injective modules is \hil{constructively neutral}.
  \end{itemize}
  \pause

>>>>

  An informative and entertaining primer on constructive mathematics can be
  found in the linked talk recording by Andrej Bauer or his
  \fixedhref{https://www.ams.org/journals/bull/2017-54-03/S0273-0979-2016-01556-4/S0273-0979-2016-01556-4.pdf}{written
  notes} on the subject. Don't worry, the standard proof that~$\sqrt{2}$ is not rational is
  perfectly fine in constructive mathematics.
  }
\end{frame}

@@

  \begin{itemize}
    \small
    \item It's consistent with \textbf{ZF} that there are no injective modules
    \href{https://www.ams.org/journals/tran/1979-255-00/S0002-9947-1979-0542870-6/S0002-9947-1979-0542870-6.pdf}{[Blass 1979]}.
    \item The existence of enough injective modules is \hil{constructively neutral}.
  \end{itemize}
  \pause
